What is the Effect of X on Y?

### 2023-10-05 latex-slides/slides.tex
Small tweaks to latex slides
Update slides to have fallback colors
Update slides template (no warnings)

\documentclass[aspectratio=169]{beamer}
% \documentclass[aspectratio=43]{beamer}

% Define `accent`/`accent2` colors for theme customization
\definecolor{accent}{HTML}{006896}
\definecolor{accent2}{HTML}{E64173}

% Beamer theme
\input{preamble.tex}

% Title --------------------------------------------
\title{What is the Effect of X on Y?}
\date{\today}
\author{Kyle Butts}

% Set-up Bibliography ------------------------------
\addbibresource{references.bib}

@@

\begin{frame}{Components}{Citations}
    Topic 1: Spatial Frictions
    \begin{citecolor}
        [\citet{Fajgelbaum_Morales_Serrato_Zidar_2018}, \citet{Hsieh_Moretti_2019}, and \citet{Moretti_2011}]
    \end{citecolor}

    \vspace{5mm}
    Topic 2: Blah 
    \begin{citecolor}
        [\citet{Suárez_Serrato_Zidar_2016}]
    \end{citecolor}
\end{frame}

\begin{frame}{Components}{Blocks}
  \begin{block}{}
    The main specificaiton is as follows: 
    $$
      y_{it} = X_{it} \beta + \mu_i + \varepsilon_{it}
    $$
    With $\mu_i$ being unit fixed effects.
  \end{block}
\end{frame}

@@

\begin{frame}[plain]
  \bgNavy{Test word} with \textbackslash bgNavy\{...\}

  \vspace{2.5mm}
  \bgPurple{Test word} with \textbackslash bgPurple\{...\}

  \vspace{2.5mm}
  \bgOrange{Test word} with \textbackslash bgOrange\{...\}

  \vspace{2.5mm}
  \bgTeal{Test word} with \textbackslash bgTeal\{...\}

  \vspace{2.5mm}
  \bgKelly{Test word} with \textbackslash bgKelly\{...\}

  \vspace{2.5mm}
  \bgRuby{Test word} with \textbackslash bgRuby\{...\}

  \vspace{2.5mm}
  \bgAlice{Test word} with \textbackslash bgAlice\{...\}

  \vspace{2.5mm}
  \bgDaisy{Test word} with \textbackslash bgDaisy\{...\}

  \vspace{2.5mm}
  \bgCoral{Test word} with \textbackslash bgCoral\{...\}

  \vspace{2.5mm}
  \bgCranberry{Test word} with \textbackslash bgCranberry\{...\}
\end{frame}

\begin{frame}{Components}{Two Columns}
    \begin{columns}[T]
    \vspace{0pt}
    \begin{column}{.50\textwidth}
        \vspace{0pt}
        {\color{accent}\rule{\linewidth}{2pt}}
        Column 1

        \begin{enumerate}
            \item Bullet points for this column that can go over lines
            \item b
            \item c
        \end{enumerate}

        \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
    \end{column}

@@

\begin{frame}{Components}{Two Columns with Figure}
    \begin{columns}[T]
    \vspace{0pt}
    \begin{column}{.6\textwidth}
        \includegraphics[width=0.9\textwidth]{img/kanagawa.jpg}

        \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
    \end{column}
    \hfill
    \begin{column}{.4\textwidth}
        \begin{itemize}
            \item A point about the figure that is potentially important.
            \item Another point about the figure that is also potentially important.
        \end{itemize}
    \end{column}
    \end{columns}
\end{frame}

@@

\begin{frame}{Table}

\begin{columns}[T]
  \vspace{0pt}
  \begin{column}{.6\textwidth}
    % Adjust Font Size to make table fit   
    \begin{table}[!htbp]
      % \caption{Regression Results} 
      \label{}

@@

              \end{tabular} 
              % Notes 
              \begin{tablenotes}
                  \item \textit{Notes.} $^{*} p<0.1$; $^{**} p<0.05$; $^{***} p<0.01$.
              \end{tablenotes}
          \end{threeparttable}
      \end{adjustbox}
    \end{table}

      \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
  \end{column}
  \hfill
  \begin{column}{.4\textwidth}
      \begin{itemize}
          \item Use \texttt{\textbackslash marktopleft\{name\}} and \texttt{\textbackslash markbottomright\{name\}} within the table to create box.
          \item Using \texttt{\textbackslash only} or \texttt{\textbackslash on} lets you conditionally display box
      \end{itemize}
  \end{column}
\end{columns}

\end{frame}

@@

\begin{frame}{Figure}{}
    \begin{center}
        \resizebox{0.85\columnwidth}{!}{%
            \includegraphics{img/kanagawa_16_9.png}
        }
    \end{center}
\end{frame}

@@

\begin{frame}{Appendix Slide}\label{appendix1}
\begin{table}
    \caption{Summary Statistics}
    \label{appendix_summ_stat}
    \begin{adjustbox}{max width = \textwidth, width = 0.7\textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} lccccccc @{}} 
                \toprule
                Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
                \hline \\[-1.8ex] 
                rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
                complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
                privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
                learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
                raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
                critical & 30 & 74.767 & 9.895 & 49 & 69.2 & 80 & 92 \\ 
                advance & 30 & 42.933 & 10.289 & 25 & 35 & 47.8 & 72 \\ 
                \bottomrule
            \end{tabular} 
            % Notes 
            \begin{tablenotes}
                \item \textit{Notes.} Using R base dataframe attitude.
            \end{tablenotes}
        \end{threeparttable}
    \end{adjustbox}
\end{table}

    \hyperlink{main1}{\beamergotobutton{Back to Main}}
\end{frame}
\end{document}

>>>>

\documentclass[aspectratio=169,t]{beamer}
% \documentclass[aspectratio=43]{beamer}
\input{preamble.tex}

% Define `accent`/`accent2` colors for theme customization
\definecolor{accent}{HTML}{006896}
\definecolor{accent2}{HTML}{695693}

\title{What is the Effect of X on Y?}
\date{\today}
\author{Kyle Butts}

\addbibresource{references.bib}

@@

\begin{frame}{Components}{Citations}
    Topic 1: Spatial Frictions
    \citecolor{
      [\citet{Fajgelbaum_Morales_Serrato_Zidar_2018}, \citet{Hsieh_Moretti_2019}, and \citet{Moretti_2011}]
    }

    \vspace{5mm}
    Topic 2: Blah 
    \citecolor{
      [\citet{Suárez_Serrato_Zidar_2016}]
    }
\end{frame}

\begin{frame}{Components}{Blocks}
  \begin{block}{Theorem 1}
    The main specificaiton is as follows: 
    $$
    y_{it} = X_{it} \beta + \mu_i + \varepsilon_{it}
    $$
  \end{block}
\end{frame}

@@

\begin{frame}{Components}{Background Colors}
  \bgNavy{Test word} with \textbackslash bgNavy\{...\}

  \bgPurple{Test word} with \textbackslash bgPurple\{...\}

  \bgOrange{Test word} with \textbackslash bgOrange\{...\}

  \bgTeal{Test word} with \textbackslash bgTeal\{...\}

  \bgKelly{Test word} with \textbackslash bgKelly\{...\}

  \bgRuby{Test word} with \textbackslash bgRuby\{...\}

  \bgAlice{Test word} with \textbackslash bgAlice\{...\}

  \bgDaisy{Test word} with \textbackslash bgDaisy\{...\}

  \bgCoral{Test word} with \textbackslash bgCoral\{...\}

  \bgCranberry{Test word} with \textbackslash bgCranberry\{...\}
\end{frame}

\begin{frame}{Components}{Two Columns}
  \begin{columns}[T]
    \begin{column}{.50\textwidth}
        \vspace{0pt}
        {\color{accent}\rule{\linewidth}{2pt}}
        Column 1

        \begin{enumerate}
            \item Bullet points for this column that can go over lines
            \item b
            \item c
        \end{enumerate}
    \end{column}

@@

\begin{frame}{Components}{Two Columns with Figure}
  \begin{columns}[T]
    \vspace{0pt}
    \begin{column}{.6\textwidth}
        \includegraphics[width=0.9\textwidth]{img/kanagawa.jpg}
    \end{column}
    \hfill
    \begin{column}{.4\textwidth}
        \begin{itemize}
            \item A point about the figure that is potentially important.
            \item Another point about the figure that is also potentially important.
        \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Table}
  \begin{columns}[T]
    \begin{column}{.6\textwidth}
      % Adjust Font Size to make table fit   
      \begin{table}[!htbp]
        % \caption{Regression Results}

@@

                \end{tabular} 
                % Notes 
                \begin{tablenotes}
                    \item \textit{Notes.} $^{*} p<0.1$; $^{**} p<0.05$; $^{***} p<0.01$.
                \end{tablenotes}
            \end{threeparttable}
        \end{adjustbox}
      \end{table}
    \end{column}
    \hfill
    \begin{column}{.4\textwidth}
        \begin{itemize}
            \item Use \texttt{\textbackslash marktopleft\{name\}} and \texttt{\textbackslash markbottomright\{name\}} within the table to create box.
            \item Using \texttt{\textbackslash only} or \texttt{\textbackslash on} lets you conditionally display box
        \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Figure}{}
  \begin{adjustbox}{width = 0.7\textwidth, center}
    \includegraphics{img/kanagawa_16_9.png}
  \end{adjustbox}
\end{frame}

@@

\begin{frame}{Appendix Slide}{\hyperlink{main1}{\beamergotobutton{Back to Main}}}\label{appendix1}
  \begin{table}
    \caption{Summary Statistics}
    \label{appendix_summ_stat}
    \begin{adjustbox}{max width = \textwidth, width = 0.7\textwidth, center}
      \begin{threeparttable}
        \begin{tabular}{@{} lccccccc @{}} 
          \toprule
          Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Pctl(25)} & \multicolumn{1}{c}{Pctl(75)} & \multicolumn{1}{c}{Max} \\ 
          \hline \\[-1.8ex] 
          rating & 30 & 64.633 & 12.173 & 40 & 58.8 & 71.8 & 85 \\ 
          complaints & 30 & 66.600 & 13.315 & 37 & 58.5 & 77 & 90 \\ 
          privileges & 30 & 53.133 & 12.235 & 30 & 45 & 62.5 & 83 \\ 
          learning & 30 & 56.367 & 11.737 & 34 & 47 & 66.8 & 75 \\ 
          raises & 30 & 64.633 & 10.397 & 43 & 58.2 & 71 & 88 \\ 
          \bottomrule
        \end{tabular}

        \begin{tablenotes}
            \item \textit{Notes.} Using R base dataframe attitude.
        \end{tablenotes}
      \end{threeparttable}
    \end{adjustbox}
  \end{table}
\end{frame}

\end{document}
